\documentclass[dvips,12pt]{article}

\usepackage[pdftex]{graphicx}
\usepackage{url}

% These are additional packages for "pdflatex", graphics, and to include
% hyperlinks inside a document.

\setlength{\oddsidemargin}{0.25in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{0in}
\setlength{\textheight}{8.5in}

% These force using more of the margins that is the default style

\begin{document}
	
	\title{A Proposal for E-WASTE Management}
	\author{Guoliang Xue}
	\date{\today}
	\maketitle
	
	\section*{Key Points}
	
	People are facing a hazardous problem in the modern era, more specifically saying, there are 20-50 million tons of e-waste being produced per year around the world, and this trend is still keeping going up. 
	
	The e-waste originally appeared in the developed countries, but now expanded to the developing countries, even less developed countries, which brings them both advantage and disadvantage.
	
	The reason why e-waste has such contradictory traits mainly lies on the two aspects of e-waste, which are supposed to be treated respectively:
	\begin{itemize}
		\item Poisonous parts in the e-waste.(disadvantages)
		\item Valuable parts in the e-waste.(advantages)
	\end{itemize}
   Therefore, how to maximize the advantages, meanwhile minimize the disadvantage becomes a priority for those suffering countries.
   
   Traditional ways to deal with e-waste will consist of four procedures: Recycling, Landfills, Composition of e-waste, and Security issues.
   The paper also provides several approaches: Life Cycle Assessment, Material Flow Analysis, Multi-Criteria Analysis , Extended Producer Responsibility, Health Implications.
   
   A good management system should apply above approaches into procedures. How can we innovate over the traditional method and put forward a more scientific and efficient way could be a interesting proposal for our final project.
   
   
   
   \begin{thebibliography}{99}
   	
   	\bibitem{gonzalez2012} 
   	Munam Ali Shah,	
   	Rakhshanda Batool,	
   	{An Overview of Electronic Waste Management, Practices and Impending Challenges},
   	International Journal of Computer Applications (0975 – 8887), {\bf Volume 125}, No.2 (2015).
   	
   \end{thebibliography}
   
	
\end{document}