\section{Related Work}

\subsection{E-Waste Related}

%\subsection{Jonas Mattes}
\input{related/related-Robinson2009} 

%\subsection{Anita Baier}
\input{related/related-law-and-projects} 

%\subsection{Bruno M\"uller}
\input{related/related-global-perspectives-on-e-waste}

%\subsection{Changkun Ou}
\input{related/related-plambeck2009}

%\subsection{Zhe Li}
\input{related/related-EU-ETS}

%\subsection{An}
\input{related/related-kahhat2008exploring}

%\subsection{Guoliang Xue}
\input{related/related-e-waste-management}

\subsection{System Currently}
There are already some existing E-Waste system. For example, the EWSI is a company that offers customized end-to-end solutions in IT Asset Recovery, E-Waste Management, and Electronics Reverse Logistics. It can provide a variety of containers for onsite collection, audit and asset registration services on pickup, and either dedicated or consolidated routes and storage prior to processing. Their E-Waste system can also provide site clearance and decommissioning services.

To close the electronics loop, EWSI takes the residual e-waste streams after refurbishment and component harvesting (as well as any whole assets designated for destruction by their owners) and uses state-of-the-art engineering to break these down into segregated material streams for processing, refining, and maximum extraction to produce new manufacturing input.

The EWSI's E-Waste system operates with a zero-landfill objective and uses a variety of processes to generate up to twenty different streams of recyclate that are converted into new raw materials by intelligent and environmentally friendly downstream refining. They recover maximum value from these materials, including glass, plastics, ferrous and non-ferrous metals, precious metals, and platinum group metals.

EWSI offers the highest standards in data security. That provides custom solutions, using in-house resources or those of their affiliate network, based around the following processes: DOD-compliant overwriting, degaussing, encryption, long-term storage and physical destruction. Their collection and transportation services are secure and transparent.

Another example is from the U.S. which is establishing the importance of developing public response for E-Waste system and the U.S. has already legislated and implemented electronic recycling systems. Several tools including Life Cycle Assessment (LCA), Material Flow Analysis (MFA), Multi Criteria Analysis (MCA) and Extended Producer Responsibility (EPR) have been developed to manage e-wastes especially in developed countries\cite{kiddee2013electronic}. Currently, different systems for different kinds of E-Waste system have been implemented and used. A beverage container recycling program, commonly referred
to as a “bottle bill,” is one important example of a successful deposit-refund system. The “bottle bill” is a system that encourages consumers to return beverage containers by providing a refund on the deposit, and this system is considered by many stakeholders as a successful recycling program that should be expanded as a federal policy. The refund value of the container provides a monetary incentive to return the container for recycling\cite{kahhat2008exploring}. This is a very good solution for the design of new E-Waste system.